---
title: "Assigment - kNN DIY"
author:
  - Lotte Ulrich - Author
  - Evert-Jan Heikoop - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---



```{r}
library(Tidyverse)
library(googlesheets4)
Library(class)
library(caret)
```

---

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.

## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read.csv(url)

str(rawDF)
```

## Data Preparation (1/2)
```{r}
cleanDF <- rawDF[-1]
head(cleanDF)

cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
propDiag
```
```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0", "1"), labels = c("No occupancy","Occupancy")) %>% relevel("Occupancy")
head(cleanDF, 10)

summary(cleanDF[c("Temperature", "Humidity", "Light", "Co2", "HumidityRatio")])

normalize <- function(x) { 
  return ((x - min(x)) / (max(x) - min(x)))}
```
```{r}
cleanDF <- cleanDF[, c(6,1,4,3,2,5)]

head(cleanDF)
```

```{r}
testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")

cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet2))
```


## Data preparation (2/2) 
```{r}
nCols <- dim(cleanDF)[2]
cleanDFn <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[c("V1", "V2", "V3", "V4", "V5")])
```

```{r}
trainDF_feat <- cleanDF_n[1:471,  ]
testDF_feat <- cleanDF_n[472:843,  ]
```

```{r}
trainDF_labels <- cleanDF[1:471,  1]
testDF_labels <- cleanDF[472:843,  1]
```

## Modeling
```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_test_pred)
```

```{r}
format(cleanDF_n)
```

```{r}
cleanDF_n.numeric <- cleanDF_n[,2:5]
cleanDF_n.classes <- cleanDF_n[,1]

str(cleanDF_n); summary(cleanDF_n)
```


## Evaluation and Deployment
```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels, positive = NULL, dnn = c("Prediction", "True"))
```


reviewer adds suggestions for improving the model

## Error 1
library(Tidyverse)
library(googlesheets4)
Library(class)
library(caret)

## Fix Error 1
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)

small letter l in library instead of the capital letter L
small letter t in tidyverse instead of capital letter T

## Error 2
summary(cleanDF[c("Temperature", "Humidity", "Light", "Co2", "HumidityRatio")])

## Fix Error 2

summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2", "HumidityRatio")])

Small letter in Co2 should be a capital

## Error 3

cleanDF <- cleanDF[, c(6,1,4,3,2,5)]

## Fix Error 3

cleanDF <- cleanDF[, c(6,1,2,3,4,5)]

order of numbers should be be changed

## Error 4

nCols <- dim(cleanDF)[2]
cleanDFn <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

## Fix Error 4

nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

cleanDFn needed an underscore correct would be cleanDF_n

## Error 5

trainDF_feat <- cleanDF_n[1:471,  ]
testDF_feat <- cleanDF_n[472:843,  ]

trainDF_labels <- cleanDF[1:471,  1]
testDF_labels <- cleanDF[472:843,  1]

## Fix Error 5

trainDF_feat <- cleanDF_n[1:4071,  ]
testDF_feat <- cleanDF_n[4072:8143,  ]

trainDF_labels <- cleanDF[1:4071,  1]
testDF_labels <- cleanDF[4072:8143,  1]

the 471,472,843 were wrong they needed to be 4071, 4072, 8143

## tip
I would work in more chunks and give each chunk a small title on what you are doing so if you run into a problem it is easier to find the problem.